---
title: "ASA Results"
output:
  bookdown::pdf_document2:
    #fig_caption: yes
    toc: no #yes
    number_sections: false
---

```{r setup, include = FALSE, message=FALSE, warning=FALSE}

options(kableExtra.latex.load_packages = FALSE)

source("../r/helper.r")
source("../r/functions.r")

library(TMB)
library(kableExtra)

options(scipen = 9999, digits = 4)

# Data
ts <- read_csv("../data/tmb_inputs/abd_indices.csv")        # time series
age <- read_csv("../data/tmb_inputs/agecomps.csv")          # age comps
bio <- read_csv("../data/tmb_inputs/maturity_sexratio.csv") # proportion mature and proportion-at-age in the survey
waa <- read_csv("../data/tmb_inputs/waa.csv")               # weight-at-age

# Starting values
finits <- read_csv("../data/tmb_inputs/inits_f_devs.csv")   # log F devs
rinits <- read_csv("../data/tmb_inputs/inits_rec_devs.csv") # log rec devs

# Model dimensions
syr <- min(ts$year)       # model start year
lyr <- max(ts$year)       # end year
nyr <- length(syr:lyr)    # number of years        
rec_age <- min(waa$age)   # recruitment age                  
plus_group <- max(waa$age)            # plus group age
nage <- length(rec_age:plus_group)    # number of ages
# number of years to project forward *FLAG* eventually add to cpp file,
# currently just for graphics
nproj <- 1        

# Subsets
mr <- filter(ts, !is.na(mr))
fsh_cpue <- filter(ts, !is.na(fsh_cpue))
srv1_cpue <- filter(ts, !is.na(srv1_cpue))
srv2_cpue <- filter(ts, !is.na(srv2_cpue))
fsh_age <- filter(age, Source == "Fishery")
srv_age <- filter(age, Source == "Survey")
```

```{r model_objects, include = FALSE, message=FALSE, warning=FALSE}

# Structure data for TMB - must use same variable names as .cpp
data <- list(
  
  # Model dimensions
  nyr = nyr,
  nage = nage,
  
  # Switch recruitment estimation: 0 = penalized likelihood (fixed sigma_r), 1 =
  # random effects
  random_rec = 1,
  
  # Time varying parameters - each vector contains the terminal years of each time block
  blks_fsh_sel = c(16, 37), # fishery selectivity 
  blks_srv_sel = c(16, 37), # survey selectivity
  
  # Fixed parameters
  M = 0.1,
  sigma_catch = 0.05,
  sigma_cpue = 0.1,
  omega = 50,
  
  # Fxx levels that correspond with spr_Fxx in Parameter section
  Fxx_levels = c(0.35, 0.40, 0.50),
  
  # Priors ("p_" denotes prior)
  p_fsh_q = 0.001,
  sigma_fsh_q = 1,
  p_srv1_q = 0.001,
  sigma_srv1_q = 1,
  p_srv2_q = 0.001,
  sigma_srv2_q = 1,
  p_mr_q = 1.0,
  sigma_mr_q = 0.01,
  
  # Weights on likelihood components ("wt_" denotes weight)
  wt_catch = 1.0,
  wt_fsh_cpue = 1.0,
  wt_srv1_cpue = 1.0,
  wt_srv2_cpue = 1.0,
  wt_mr = 1.0,
  wt_fsh_age = 1.0,
  wt_srv_age = 1.0,
  wt_rec_like = 0.1,
  wt_fpen = 0.1,
  wt_spr = 200,
  
  # Catch
  data_catch = ts$catch,
  
  # Mark-recapture estimates
  nyr_mr = n_distinct(mr, mr),
  yrs_mr = mr %>% distinct(index) %>% pull(),
  data_mr = pull(mr, mr),
  sigma_mr = pull(mr, mr_sd), # rep(0.05, 10),
  
  # Fishery CPUE
  nyr_fsh_cpue = fsh_cpue %>% n_distinct(fsh_cpue),
  yrs_fsh_cpue = fsh_cpue %>% distinct(index) %>% pull(),
  data_fsh_cpue = pull(fsh_cpue, fsh_cpue),
  
  # Survey CPUE 1-hr soak time
  nyr_srv1_cpue = srv1_cpue %>% n_distinct(srv1_cpue),
  yrs_srv1_cpue = srv1_cpue %>% distinct(index) %>% pull(),
  data_srv1_cpue = pull(srv1_cpue, srv1_cpue),
  
  # Survey CPUE 3+ hr soak time
  nyr_srv2_cpue = srv2_cpue %>% n_distinct(srv2_cpue),
  yrs_srv2_cpue = srv2_cpue %>% distinct(index) %>% pull(),
  data_srv2_cpue = pull(srv2_cpue, srv2_cpue),
  
  # Timing in month fractions
  spawn_month = 2/12, # Feb
  srv_month = 7/12,   # Jul
  fsh_month = 8/12,   # Aug
  
  # Proportion mature-at-age
  prop_mature = bio$prop_mature,
  
  # Proportion female-at-age in the survey
  prop_fem = bio$prop_fem,
  
  # Weight-at-age
  data_fsh_waa = filter(waa, Source == "Fishery (sexes combined)") %>% pull(weight),
  data_srv_waa = filter(waa, Source == "Survey (sexes combined)") %>% pull(weight),
  data_fem_waa = filter(waa, Source == "Survey females (spawning biomass)") %>% pull(weight),
  
  # Fishery age comps
  nyr_fsh_age = fsh_age %>% distinct(year) %>% nrow(),
  yrs_fsh_age = fsh_age %>% distinct(index) %>% pull(),
  data_fsh_age = fsh_age %>% select(-c(year, index, Source)) %>% as.matrix(),
  
  # Survey age comps
  nyr_srv_age = srv_age %>% distinct(year) %>% nrow(),
  yrs_srv_age = srv_age %>% distinct(index) %>% pull(),
  data_srv_age = srv_age %>% select(-c(year, index, Source)) %>% as.matrix()
)

# Parameters ----

# Parameter starting values
parameters <- list(
  
  dummy = 0,   # Used for troubleshooting model               
  
  # Selectivity
  fsh_sel50 = rep(3.52, length(data$blks_fsh_sel)),
  fsh_sel95 = rep(5.43, length(data$blks_fsh_sel)),
  srv_sel50 = rep(3.86, length(data$blks_srv_sel)),
  srv_sel95 = rep(5.13, length(data$blks_srv_sel)), 
  
  # Catchability
  fsh_logq = -3.6726,
  srv1_logq = -3.8929,
  srv2_logq = -2.4019,
  mr_logq = -0.0001,
  
  # Recruitment (rec_devs include a parameter for all ages in the inital yr plus
  # age-2 in all yrs, nyr+nage-2)
  log_rbar = -0.3798,
  log_rec_devs = rinits$rinits,
  log_sigma_r = 0.1823216, # Federal value of 1.2 on log scale, Sigler et al. (2002)
  
  # Fishing mortality
  log_Fbar = -1.8289,
  log_F_devs = finits$finits,
  
  # SPR-based fishing mortality rates, i.e. the F at which the spawning biomass
  # per recruit is reduced to xx% of its value in an unfished stock
  spr_Fxx = c(0.128, 0.105, 0.071)       # e.g. F35, F40, F50
  
)

# Parameter bounds
lower <- c(             # Lower bounds
  rep(0.1, length(data$blks_fsh_sel) + length(data$blks_srv_sel)),          # Selectivity
  rep(-15, 4),          # Catchability log_q
  -Inf,                 # log mean recruitment
  rep(-10, nyr+nage-2), # log recruitment deviations
  -Inf,                 # log sigma R  
  -Inf,                 # Mean log F
  rep(-15, nyr)         # log F deviations
)

upper <- c(             # Upper bounds
  rep(10, length(data$blks_fsh_sel) + length(data$blks_srv_sel)),           # Selectivity
  rep(5, 4),            # Catchability q
  Inf,                  # log mean recruitment
  rep(10, nyr+nage-2),  # log recruitment deviations
  Inf,                  # log sigma R
  Inf,                  # Mean log F  
  rep(15, nyr)          # log F deviations  
)

```


```{r run_mod, include = FALSE, message=FALSE, warning=FALSE}
# Use map to turn off parameters, either for testing with dummy, phasing, or to
# fix parameter values

# When testing the code
# map <- list(fsh_sel50 = rep(factor(NA), length(data$blks_fsh_sel)),
#             fsh_sel95 = rep(factor(NA), length(data$blks_fsh_sel)),
#             srv_sel50 = rep(factor(NA), length(data$blks_srv_sel)),
#             srv_sel95 = rep(factor(NA), length(data$blks_srv_sel)),
#             fsh_logq = factor(NA), srv1_logq = factor(NA),
#             srv2_logq = factor(NA), mr_logq = factor(NA),
#             log_rbar = factor(NA), log_rec_devs = rep(factor(NA), nyr+nage-2),
#             log_Fbar = factor(NA), log_F_devs = rep(factor(NA), nyr),
#             spr_Fxx = rep(factor(NA), length(data$Fxx_levels)))

# Compile
compile("mod.cpp")
dyn.load(dynlib("mod"))

# Setup random effects
random_vars <- c()
if (data$random_rec == 1) {
  random_vars <- c("log_rec_devs")
}
# Estimate everything at once
map <- list(dummy=factor(NA))

# Fix parameter if sigma_r is not estimated via random effects
if(data$random_rec == 0) {
  map$log_sigma_r <- factor(NA)
}

model <- MakeADFun(data, parameters, DLL = "mod", 
                   silent = TRUE, map = map,
                   random = random_vars)

fit <- nlminb(model$par, model$fn, model$gr,
              control=list(eval.max=100000,iter.max=1000),
              lower = lower, upper = upper)

# for (i in 1:3){
#   fit <- nlminb(model$env$last.par.best, model$fn, model$gr)}

best <- model$env$last.par.best
# print(as.numeric(best))
rep <- sdreport(model)
# print(best)

est <- stack(as.list(rep, what = "Estimate")) %>% 
  select(Parameter = ind, Estimate = values) %>% 
  bind_cols(stack(as.list(rep, what = "Std")) %>% 
  select(`SE` = values))

```

## Parameter estimates

```{r test5, echo = FALSE}
kable(est, "latex",  longtable = TRUE) %>% #booktabs = TRUE,
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

## Catchability

Estimates on natural scale

Fishery q:  `r exp(as.list(rep, what = "Estimate")$fsh_logq)`

Survey (1-hr soak) q:  `r exp(as.list(rep, what = "Estimate")$srv1_logq)`

Survey (3+hr soak) q:  `r exp(as.list(rep, what = "Estimate")$srv2_logq)`

Mark-recapture q:  `r exp(as.list(rep, what = "Estimate")$mr_logq)`


## Likelihood components

Catchability priors: `r model$report()$priors`

Catch: `r model$report()$catch_like`

Abundance indices (fsh, srv1, srv2, mr): `r model$report()$index_like`

Age comp `r model$report()$age_like`

Multinomial offsets `r model$report()$offset`

Penalty on fishing mortality deviations: `r model$report()$fpen`

Penalty on recruitment deviations: `r model$report()$rec_like`

**Total likelihood**: `r model$report()$obj_fun`

## Time series of catch and abundance indices

```{r plot_ts, echo=FALSE, fig.height = 6.5, fig.width = 6, message=FALSE, warning=FALSE}

# Catch 
ts$pred_catch <- model$report()$pred_catch
axis <- tickr(ts, year, 5)
ggplot(ts, aes(x = year)) +
  geom_ribbon(aes(ymin = catch - data$sigma_catch * catch, 
                  ymax = catch + data$sigma_catch * catch),
              alpha = 0.2,  fill = "grey") +
  geom_point(aes(y = catch)) +
  geom_line(aes(y = pred_catch), colour = "grey") +
  scale_x_continuous(breaks = axis$breaks, labels = axis$labels) +
  labs(x = "", y = "\n\nCatch\n(round mt)") -> p_catch

# Fishery cpue
fsh_cpue$pred_fsh_cpue <- model$report()$pred_fsh_cpue
ggplot(fsh_cpue, aes(x = year)) +
  geom_ribbon(aes(ymin = fsh_cpue - data$sigma_cpue * fsh_cpue, 
                  ymax = fsh_cpue + data$sigma_cpue * fsh_cpue),
              alpha = 0.2,  fill = "grey") +
  geom_point(aes(y = fsh_cpue)) +
  geom_line(aes(y = pred_fsh_cpue), colour = "grey") +
  scale_x_continuous(breaks = axis$breaks, labels = axis$labels) +
  labs(x = "", y = "\n\nFishery CPUE\n(round kg/hook)") -> p_fsh

# Survey cpue
ts %>% 
  select(year, contains("srv")) %>% 
  gather("survey", "obs", c("srv1_cpue", "srv2_cpue")) %>%
  na.omit() %>%
  mutate(survey = ifelse(survey == "srv1_cpue", "1-hr soak", "3+hr soak"),
         pred = c(model$report()$pred_srv1_cpue,
                  model$report()$pred_srv2_cpue)) -> srv

ggplot(srv, aes(x = year)) +
  geom_ribbon(aes(ymin = obs - data$sigma_cpue * obs, 
                  ymax = obs + data$sigma_cpue * obs),
              alpha = 0.2,  fill = "grey") +
  geom_point(aes(y = obs, shape = survey)) +
  geom_line(aes(y = pred, group = survey), colour = "grey") +
  geom_vline(xintercept = 1997, linetype = 2, colour = "grey") +
  # scale_y_continuous(limits = c(0.05, 0.45)) +
  scale_x_continuous(breaks = axis$breaks, labels = axis$labels) +
  labs(y = "\n\nSurvey CPUE\n(number/hook)", x = NULL, shape = NULL) +
  theme(legend.position = c(.1, .8)) -> p_srv

# Mark recapture 
mr %>% 
  mutate(pred_mr = model$report()$pred_mr) %>% 
  select(year, pred_mr) %>% 
  right_join(ts %>%
               select(year, mr, mr_sd) %>%
               mutate(pred_mr_all = model$report()$pred_mr_all)) -> mr_plot

ggplot(mr_plot, aes(x = year)) +
  geom_errorbar(aes(x = year, ymin = mr - 2 * mr_sd, ymax = mr + 2 * mr_sd),
              colour = "grey", width = 0) +
  geom_point(aes(y = mr)) +
  geom_line(aes(y = pred_mr, group = 1), colour = "grey") +
  # geom_point(aes(y = pred_mr), colour = "grey") +
  geom_line(aes(y = pred_mr_all, group = 1), lty = 2, colour = "grey") +
  scale_x_continuous( breaks = axis$breaks, labels = axis$labels) +
  labs(x = "", y = "\n\nAbundance\n(millions)") -> p_mr

plot_grid(p_catch, p_fsh, p_srv, p_mr, ncol = 1, align = 'hv', 
          labels = c('(A)', '(B)', '(C)', '(D)'))

```

## Residuals for time series of catch and abundance indices

Standardized residuals:

```{r plot_resids_ts, echo=FALSE, fig.height = 6.5, fig.width = 6, message=FALSE, warning=FALSE}
ts %>% 
  mutate(catch_resid = catch - pred_catch,
         catch_sresid = catch_resid / sd(catch_resid)) -> ts

ggplot(ts, aes(x = year, y = catch_sresid)) + 
  geom_hline(yintercept = 0, colour = "grey", size = 1) +
  geom_segment(aes(x = year, xend = year, y = 0, yend = catch_resid), 
               size = 0.2, colour = "grey") +
  geom_point() +
  labs(x = "", y = "\n\nCatch\nresiduals") +
  scale_x_continuous(breaks = axis$breaks, labels = axis$labels) -> r_catch

# Fishery cpue resids
fsh_cpue %>% 
  mutate(fsh_cpue_resid = fsh_cpue - pred_fsh_cpue,
         fsh_cpue_sresid = fsh_cpue_resid / sd(fsh_cpue_resid)) -> fsh_cpue

ggplot(fsh_cpue, aes(x = year, y = fsh_cpue_sresid)) + 
  geom_hline(yintercept = 0, colour = "grey", size = 1) +
  geom_segment(aes(x = year, xend = year, y = 0, yend = fsh_cpue_resid), 
               size = 0.2, colour = "grey") +
  geom_point() +
  labs(x = "", y = "\n\nFishery CPUE\nresiduals") +
  scale_x_continuous(breaks = axis$breaks, labels = axis$labels) -> r_fsh

# Survey cpues resids
srv %>% 
  mutate(srv_cpue_resid = obs - pred,
         srv_cpue_sresid = srv_cpue_resid / sd(srv_cpue_resid)) -> srv

ggplot(srv, aes(x = year, y = srv_cpue_sresid, shape = survey)) + 
  geom_hline(yintercept = 0, colour = "grey", size = 1) +
  geom_segment(aes(x = year, xend = year, y = 0, yend = srv_cpue_resid), 
               size = 0.2, colour = "grey") +
  geom_point() +
  labs(x = "", y = "\n\nSurvey CPUE\nresiduals", shape = NULL) +
  scale_x_continuous(breaks = axis$breaks, labels = axis$labels) +
  theme(legend.position = "none") +
  geom_vline(xintercept = 1997, linetype = 2, colour = "grey") -> r_srv

# Mark-recapture abundance estimate resids
mr_plot %>% 
  mutate(mr_resid = mr - pred_mr,
         mr_sresid = mr_resid / sd(mr_resid)) -> mr_plot

ggplot(mr_plot, aes(x = year, y = mr_sresid)) + 
  geom_hline(yintercept = 0, colour = "grey", size = 1) +
  geom_segment(aes(x = year, xend = year, y = 0, yend = mr_resid), 
               size = 0.2, colour = "grey") +
  geom_point() +
  labs(x = "", y = "\n\nMR abundance\nresiduals\n") +
  scale_x_continuous(breaks = axis$breaks, labels = axis$labels) -> r_mr

plot_grid(r_catch, r_fsh, r_srv, r_mr, ncol = 1, align = 'hv', 
          labels = c('(A)', '(B)', '(C)', '(D)'))
```

## Derived time series of recruitment, abundance, and biomass

```{r plot_derivedvars, echo=FALSE, fig.height = 8, fig.width = 6, message=FALSE, warning=FALSE}
ts %>% 
  # Add another year to hold projected values
  full_join(data.frame(year = max(ts$year) + nproj)) %>%
  # For ts by numbers go divide by 1e6 to get values in millions, for biomass
  # divide by 1e3 to go from kg to mt
  mutate(Fmort = c(model$report()$Fmort, rep(NA, nproj)),
         pred_rec = c(model$report()$pred_rec, rep(NA, nproj)) / 1e6,
         biom = model$report()$biom / 1e3,
         expl_biom = model$report()$expl_biom / 1e3,
         vuln_abd = model$report()$vuln_abd / 1e6,
         spawn_biom = model$report()$spawn_biom / 1e3,
         exploit = catch / expl_biom / 1e3) -> ts

p <- ggplot(ts, aes(x = year)) +
  scale_x_continuous(breaks = axis$breaks, labels = axis$labels) +
  scale_y_continuous(label = scales::comma)

# Recruitment
p + geom_point(aes(y = pred_rec)) +
  geom_line(aes(y = pred_rec, group = 1)) +
  labs(x = "", y = "\n\nAge-2 recruits\n(millions)") -> p_rec

# Total biomass
p + geom_point(aes(y = biom)) +
  geom_line(aes(y = biom, group = 1)) +
  labs(x = "", y = "\n\nTotal\nbiomass (mt)") -> p_biom

# Exploitable biomass (to fishery)
p + geom_point(aes(y = expl_biom)) +
  geom_line(aes(y = expl_biom, group = 1)) +
  labs(x = "", y = "\n\nExploitatble\nbiomass (mt)") -> p_ebiom

# Vulnerable abundance (to survey)
p + geom_point(aes(y = vuln_abd)) +
  geom_line(aes(y = vuln_abd, group = 1)) +
  labs(x = "", y = "\n\nVulnerable\nabundance (millions)") -> p_vabd

# Spawning biomass 
p + geom_point(aes(y = spawn_biom)) +
  geom_line(aes(y = spawn_biom, group = 1)) +
  labs(x = "", y = "\n\nSpawning\nbiomass(mt)") -> p_sbiom

plot_grid(p_rec, p_biom, p_ebiom, p_vabd, p_sbiom, ncol = 1, align = 'hv',
          labels = c('(A)', '(B)', '(C)', '(D)', '(E)'))
```

## Estimate of fishing mortality

On natural scale

```{r plot_F, echo=FALSE, message=FALSE, warning=FALSE}
p + geom_point(aes(y = Fmort)) +
  geom_line(aes(y = Fmort, group = 1)) +
  labs(x = "", y = "Fishing mortality") 

```

## Fits to age comps

```{r plot_resid_agecomps, echo=FALSE, message=FALSE, warning=FALSE}

pred_fsh_age <- as.data.frame(model$report()$pred_fsh_age)
names(pred_fsh_age) <- as.character(rec_age:plus_group)
pred_fsh_age %>% 
  mutate(Source = "Fishery",
         index = data$yrs_fsh_age) -> pred_fsh_age

pred_srv_age <- as.data.frame(model$report()$pred_srv_age)
names(pred_srv_age) <- as.character(rec_age:plus_group)
pred_srv_age %>% 
  mutate(Source = "Survey",
         index = data$yrs_srv_age) -> pred_srv_age

# Reshape age comp observations and predictions into long format, calculate
# residuals and prep results for plotting
age %>% 
  gather("age", "obs", 2:plus_group+2) %>%
  left_join(
    bind_rows(pred_fsh_age, pred_srv_age) %>% 
      gather("age", "pred", 1:41),
    by = c("Source", "index", "age")) %>% 
  group_by(Source) %>% 
  mutate(resid = obs - pred,
         # Get standardized residual (mean of 0, sd of 1)
         std_resid = resid / sd(resid),
         # Pearson's residual
         pearson = resid / sqrt(var(pred)),
         # positive or negative
         `Model performance` = ifelse(std_resid >= 0, "Observed greater than estimated",
                                      ifelse(is.na(obs), "",
                                             "Observed less than estimated")),
         Age = factor(age, levels = c("2", "3", "4", "5", "6", "7", "8",
                                      "9", "10", "11", "12", "13", "14", "15",
                                      "16", "17", "18", "19", "20", "21", "22",
                                      "23", "24", "25", "26", "27", "28", "29", "30",
                                      "31", "32", "33", "34", "35", "36", "37", "38",
                                      "39", "40", "41", "42"),
                      labels = c("2", "3", "4", "5", "6", "7", "8",
                                 "9", "10", "11", "12", "13", "14", "15",
                                 "16", "17", "18", "19", "20", "21", "22",
                                 "23", "24", "25", "26", "27", "28", "29", "30",
                                 "31", "32", "33", "34", "35", "36", "37", "38",
                                 "39", "40", "41", "42+")))  -> agecomps

# Custom axes
axis <- tickr(agecomps, year, 5)
age_labs <- c("", "", "", "5", "", "", "", "", "10", "", "", "", "", "15",
              "", "", "", "", "20", "", "", "", "", "25", "", "",
              "", "", "30", "", "", "", "", "35", "", "", "", "",
              "40", "", "") 

ggplot(agecomps, aes(x = Age, y = year, size = std_resid,
                     fill = `Model performance`)) + 
  # geom_hline(yintercept = seq(2000, 2015, by = 5), colour = "grey", linetype = 3, alpha = 0.7) +  
  geom_point(shape = 21, colour = "black") +
  scale_size(range = c(0, 4.5)) +
  facet_wrap(~ Source) +
  labs(x = '\nAge', y = '') +
  guides(size = FALSE) +
  scale_fill_manual(values = c("black", "white")) +
  scale_x_discrete(breaks = unique(agecomps$Age), labels = age_labs) +
  scale_y_continuous(breaks = axis$breaks, labels = axis$labels) +
  theme(legend.position = "bottom")
```

## Fits to fishery age comps

```{r plot_fsh_age, echo=FALSE, fig.height = 8, fig.width = 6, message=FALSE, warning=FALSE}

# Fishery
ggplot(agecomps %>% filter(Source == "Fishery")) +
  geom_bar(aes(x = Age, y = obs), 
           stat = "identity", colour = "grey", fill = "lightgrey",
           width = 0.8, position = position_dodge(width = 0.5)) +
  geom_line(aes(x = Age, y = pred, group = 1), size = 0.6) +
  facet_wrap(~ year, dir = "v", ncol = 2) +
  scale_x_discrete(breaks = unique(agecomps$Age), labels = age_labs) +
  labs(x = '\nAge', y = 'Proportion-at-age\n') 
```

## Fits to survey age comps

```{r plot_srv_age, echo=FALSE, fig.height = 8, fig.width = 6, message=FALSE, warning=FALSE}
agecomps %>% filter(Source == "Survey") %>% 
  ggplot() +
  geom_bar(aes(x = Age, y = obs), 
           stat = "identity", colour = "grey", fill = "lightgrey",
           width = 0.8, position = position_dodge(width = 0.5)) +
  geom_line(aes(x = Age, y = pred, group = 1), size = 0.6) +
  facet_wrap(~ year, dir = "v", ncol = 3) +
  scale_x_discrete(breaks = unique(agecomps$Age), labels = age_labs) +
  labs(x = '\nAge', y = 'Proportion-at-age\n')
```

## Selectivity

```{r plot_selectivity, echo=FALSE, message=FALSE, warning=FALSE}


# Extract selectivity matrices and convert to dfs and create a second index col
# as a dummy var (must supply an interval to foverlaps). Set as data.table
# object so it is searchable
sel <- model$report()$fsh_sel %>% as.data.frame() %>% 
  mutate(Selectivity = "Fishery") %>% 
  bind_rows(model$report()$srv_sel %>% as.data.frame() %>% 
              mutate(Selectivity = "Survey"))

names(sel) <- c(unique(agecomps$age), "Selectivity")

sel <- sel %>% 
  mutate(year = rep(ts$year[1:nyr], 2)) %>% 
  gather("Age", "proportion", -c(year, Selectivity)) %>% 
  mutate(year2 = year) # needed for foverlaps()

setDT(sel)

# Look up table for selectivity time blocks
blks_sel <- data.frame(Selectivity = c(rep("Fishery", length(data$blks_fsh_sel)),
                                       rep("Survey", length(data$blks_srv_sel))),
                       end = c(data$blks_fsh_sel, data$blks_srv_sel)) %>%
  left_join(ts %>%
              mutate(end = index) %>% 
              select(year, end), by = "end") %>% 
  rename(end_year = year) %>% 
  # Define start of the interval based on the end of the interval
  group_by(Selectivity) %>% 
  mutate(start_year = c(min(ts$year), head(end_year, -1) + 1)) 
  

setkey(setDT(blks_sel), Selectivity, start_year, end_year)

# Match each year to the start and end year in blks_sel
foverlaps(x = sel, y = blks_sel,
          by.x = c("Selectivity", "year", "year2"),
          type = "within") -> sel

sel <- sel %>% 
  mutate(`Time blocks` = paste0(start_year, "-", end_year),
         age = as.numeric(Age)) %>% 
  filter(age <= 15)

ggplot(sel, aes(x = age, y = proportion, colour = `Time blocks`, 
                shape = `Time blocks`, lty = `Time blocks`, group = `Time blocks`)) +
  geom_point() +
  geom_line() +
  facet_wrap(~Selectivity) +
  scale_colour_grey() +
  labs(y = "Selectivity\n", x = NULL, 
       colour = NULL, lty = NULL, shape = NULL) +
  theme(legend.position = c(.85, .15)) 


```